Making ice sheet models \\ scale properly

### 2023-01-01 talk/slides.tex
start

%\usepackage[svgnames]{xcolor}
\usepackage{hyperref}
\hypersetup{
    pdftitle = {Online optimization},
    pdfauthor = {Ed Bueler},
    pdfsubject = {},
    pdfkeywords = {}
}

@@

\section{introduction}

>>>>

%\usepackage[svgnames]{xcolor}
\usepackage{hyperref}
\hypersetup{
    pdftitle = {Making ice sheet models scale properly},
    pdfauthor = {Ed Bueler},
    pdfsubject = {},
    pdfkeywords = {}
}

@@

\section{what is an ice sheet model}

\begin{frame}{what is an ice sheet?}

\begin{itemize}
\item before numerical models \dots \emph{what} are we modeling?
\item \emph{def.} an \alert{ice sheet} is a large glacier with small thickness$/$width ratio
\item<5> it is \emph{not} sea ice
\end{itemize}

\bigskip
\begin{minipage}[t][40cm][t]{\textwidth}
\begin{center}
\includegraphics<1>[height=0.64\textheight]{images/ant-pittard2021.png}
\only<1>{\par {\scriptsize Antarctic ice sheet (Pittard et al 2021)}}
\only<2>{\vspace{15mm}}
\includegraphics<2>[width=\textwidth]{images/ant-schoofhewitt2013.png}
\only<2>{\vspace{10mm}}
\only<2>{\par {\scriptsize note vertical exageration and rough bed (Schoof \& Hewitt 2013)}}
\includegraphics<3>[height=0.64\textheight]{images/alps-seguinot2018.png}
\only<3>{\par {\scriptsize modeled Alpine ice sheet near last glacial maximum (Seguinot et al 2018)}}
\includegraphics<4>[height=0.64\textheight]{images/british-clark2022.png}
\only<4>{\par {\scriptsize modeled British-Irish ice sheet near last glacial maximum (Clark et al 2022)}}
\includegraphics<5>[height=0.70\textheight]{images/not-sea-ice.png}
\end{center}
\end{minipage}
\end{frame}
